### 2025-07-21 evaluating-prediction-accuracy.qmd
20250721 - REFs

::: {#fig-confusionMatrix}
![](images/confusionMatrix.png){fig-alt="A Two-by-Two Confusion Matrix."}

A Two-by-Two Confusion Matrix.
:::

@@

::: {#fig-confusionMatrix1}
![](images/confusionMatrix1.png){fig-alt="Example of a Two-by-Two Confusion Matrix. TP = true positives; TN = true negatives; FP = false positives; FN = false negatives."}

Example of a Two-by-Two Confusion Matrix. TP = true positives; TN = true negatives; FP = false positives; FN = false negatives.
:::

@@

::: {#fig-confusionMatrix2}
![](images/confusionMatrix2.png){fig-alt="Example of a Two-by-Two Confusion Matrix With Marginal Sums. TP = true positives; TN = true negatives; FP = false positives; FN = false negatives."}

Example of a Two-by-Two Confusion Matrix With Marginal Sums. TP = true positives; TN = true negatives; FP = false positives; FN = false negatives.
:::

@@

::: {#fig-confusionMatrix3}
![](images/confusionMatrix3.png){fig-alt="Example of a Two-by-Two Confusion Matrix With Marginal Sums and Marginal Probabilities. TP = true positives; TN = true negatives; FP = false positives; FN = false negatives; BR = base rate; SR = selection ratio."}

Example of a Two-by-Two Confusion Matrix With Marginal Sums and Marginal Probabilities. TP = true positives; TN = true negatives; FP = false positives; FN = false negatives; BR = base rate; SR = selection ratio.
:::

@@

::: {#fig-confusionMatrix4}
![](images/confusionMatrix4.png){fig-alt="Chance Expectancies in Two-by-Two Confusion Matrix. BR = base rate; SR = selection ratio."}

Chance Expectancies in Two-by-Two Confusion Matrix. BR = base rate; SR = selection ratio.
:::

>>>>

::: {#fig-confusionMatrix}
![](images/confusionMatrix.png){fig-alt="A Two-by-Two Confusion Matrix. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

A Two-by-Two Confusion Matrix. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-confusionMatrix1}
![](images/confusionMatrix1.png){fig-alt="Example of a Two-by-Two Confusion Matrix. TP = true positives; TN = true negatives; FP = false positives; FN = false negatives. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of a Two-by-Two Confusion Matrix. TP = true positives; TN = true negatives; FP = false positives; FN = false negatives. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-confusionMatrix2}
![](images/confusionMatrix2.png){fig-alt="Example of a Two-by-Two Confusion Matrix With Marginal Sums. TP = true positives; TN = true negatives; FP = false positives; FN = false negatives. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of a Two-by-Two Confusion Matrix With Marginal Sums. TP = true positives; TN = true negatives; FP = false positives; FN = false negatives. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-confusionMatrix3}
![](images/confusionMatrix3.png){fig-alt="Example of a Two-by-Two Confusion Matrix With Marginal Sums and Marginal Probabilities. TP = true positives; TN = true negatives; FP = false positives; FN = false negatives; BR = base rate; SR = selection ratio. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of a Two-by-Two Confusion Matrix With Marginal Sums and Marginal Probabilities. TP = true positives; TN = true negatives; FP = false positives; FN = false negatives; BR = base rate; SR = selection ratio. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-confusionMatrix4}
![](images/confusionMatrix4.png){fig-alt="Chance Expectancies in Two-by-Two Confusion Matrix. BR = base rate; SR = selection ratio. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Chance Expectancies in Two-by-Two Confusion Matrix. BR = base rate; SR = selection ratio. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

### 2025-07-21 factor-analysis.qmd
20250721 - REFs

::: {#fig-simpleStructure}
![](images/simpleStructure.png){fig-alt="Example of a Factor Matrix That Follows Simple Structure."}

Example of a Factor Matrix That Follows Simple Structure.
:::

@@

::: {#fig-factorSolutionSimpleStructure}
![](images/factorSolutionSimpleStructure.png){fig-alt="Example of a Factor Analysis Model That Follows Simple Structure. 'INT' = internalizing problems; 'EXT' = externalizing problems; 'TD' = thought-disordered problems."}

Example of a Factor Analysis Model That Follows Simple Structure. 'INT' = internalizing problems; 'EXT' = externalizing problems; 'TD' = thought-disordered problems.
:::

@@

::: {#fig-factorSolutionUnrotatedExample}
![](images/factorSolutionUnrotatedExample.png){fig-alt="Example of a Factor Analysis Model That Does Not Follow Simple Structure. 'INT' = internalizing problems; 'EXT' = externalizing problems; 'TD' = thought-disordered problems."}

Example of a Factor Analysis Model That Does Not Follow Simple Structure. 'INT' = internalizing problems; 'EXT' = externalizing problems; 'TD' = thought-disordered problems.
:::

@@

::: {#fig-factorMatrix}
![](images/factorMatrix.png){fig-alt="Example of a Factor Matrix."}

Example of a Factor Matrix.
:::

@@

::: {#fig-factorSolutionUnrotated}
![](images/factorSolutionUnrotated.png){fig-alt="Example of an Unrotated Factor Solution."}

Example of an Unrotated Factor Solution.
:::

@@

::: {#fig-factorMatrixRotated}
![](images/factorMatrixRotated.png){fig-alt="Example of a Rotated Factor Matrix."}

Example of a Rotated Factor Matrix.
:::

::: {#fig-factorSolutionRotated}
![](images/factorSolutionRotated.png){fig-alt="Example of a Rotated Factor Solution."}

Example of a Rotated Factor Solution.
:::

@@

::: {#fig-orthogonalRotation}
![](images/FactorAnalysis-08.png){fig-alt="Example of a Factor Structure From an Orthogonal Rotation."}

Example of a Factor Structure From an Orthogonal Rotation.
:::

@@

::: {#fig-obliqueRotation}
![](images/FactorAnalysis-09.png){fig-alt="Example of a Factor Structure From an Oblique Rotation."}

Example of a Factor Structure From an Oblique Rotation.
:::

@@

::: {#fig-factorRotation}
![](images/factorRotation.png){fig-alt="Example of a Factor Rotation of Neuroticism and Extraversion."}

Example of a Factor Rotation of Neuroticism and Extraversion.
:::

>>>>

::: {#fig-simpleStructure}
![](images/simpleStructure.png){fig-alt="Example of a Factor Matrix That Follows Simple Structure. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of a Factor Matrix That Follows Simple Structure. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-factorSolutionSimpleStructure}
![](images/factorSolutionSimpleStructure.png){fig-alt="Example of a Factor Analysis Model That Follows Simple Structure. 'INT' = internalizing problems; 'EXT' = externalizing problems; 'TD' = thought-disordered problems. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of a Factor Analysis Model That Follows Simple Structure. 'INT' = internalizing problems; 'EXT' = externalizing problems; 'TD' = thought-disordered problems. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-factorSolutionUnrotatedExample}
![](images/factorSolutionUnrotatedExample.png){fig-alt="Example of a Factor Analysis Model That Does Not Follow Simple Structure. 'INT' = internalizing problems; 'EXT' = externalizing problems; 'TD' = thought-disordered problems. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of a Factor Analysis Model That Does Not Follow Simple Structure. 'INT' = internalizing problems; 'EXT' = externalizing problems; 'TD' = thought-disordered problems. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-factorMatrix}
![](images/factorMatrix.png){fig-alt="Example of a Factor Matrix. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of a Factor Matrix. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-factorSolutionUnrotated}
![](images/factorSolutionUnrotated.png){fig-alt="Example of an Unrotated Factor Solution. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of an Unrotated Factor Solution. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-factorMatrixRotated}
![](images/factorMatrixRotated.png){fig-alt="Example of a Rotated Factor Matrix. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of a Rotated Factor Matrix. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

::: {#fig-factorSolutionRotated}
![](images/factorSolutionRotated.png){fig-alt="Example of a Rotated Factor Solution. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of a Rotated Factor Solution. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-orthogonalRotation}
![](images/FactorAnalysis-08.png){fig-alt="Example of a Factor Structure From an Orthogonal Rotation. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of a Factor Structure From an Orthogonal Rotation. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-obliqueRotation}
![](images/FactorAnalysis-09.png){fig-alt="Example of a Factor Structure From an Oblique Rotation. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of a Factor Structure From an Oblique Rotation. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-factorRotation}
![](images/factorRotation.png){fig-alt="Example of a Factor Rotation of Neuroticism and Extraversion. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example of a Factor Rotation of Neuroticism and Extraversion. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

### 2025-07-21 pca.qmd
20250721 - REFs

::: {#fig-correlationMatrix2}
![](images/correlationMatrix2.png){fig-alt="Example Correlation Matrix 2."}

Example Correlation Matrix 2.
:::

@@

::: {#fig-pcaVsFactorAnalysis}
![](images/pcaVsFactorAnalysis.png){fig-alt="Distinction Between Factor Analysis and Principal Component Analysis."}

Distinction Between Factor Analysis and Principal Component Analysis.
:::

>>>>

::: {#fig-correlationMatrix2}
![](images/correlationMatrix2.png){fig-alt="Example Correlation Matrix 2. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Example Correlation Matrix 2. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-pcaVsFactorAnalysis}
![](images/pcaVsFactorAnalysis.png){fig-alt="Distinction Between Factor Analysis and Principal Component Analysis. From @PetersenPrinciplesPsychAssessment."}

Distinction Between Factor Analysis and Principal Component Analysis. From @PetersenPrinciplesPsychAssessment.
:::

### 2025-07-21 research-methods.qmd
20250708 - track chunk execution times
20250717 - Conclusion sections
20250721 - REFs

@@

::: {#fig-correlationAndCausation1}
![](images/correlationAndCausation_1.png){fig-alt="Hypothesized Causal Effect Based on an Observed Association Between `X` and `Y`, Such That `X` Causes `Y`."}

Hypothesized Causal Effect Based on an Observed Association Between `X` and `Y`, Such That `X` Causes `Y`.
:::

@@

::: {#fig-correlationAndCausation2}
![](images/correlationAndCausation_2.png){fig-alt="Reverse (Opposite) Direction of Effect From the Hypothesized Effect, Where `Y` Causes `X`."}

Reverse (Opposite) Direction of Effect From the Hypothesized Effect, Where `Y` Causes `X`.
:::

@@

::: {#fig-correlationAndCausation3}
![](images/correlationAndCausation_3.png){fig-alt="Bidirectional Effect Between `X` and `Y`, such that `X` causes `Y` and `Y` causes `X`."}

Bidirectional Effect Between `X` and `Y`, such that `X` causes `Y` and `Y` causes `X`.
:::

@@

::: {#fig-correlationAndCausation4}
![](images/correlationAndCausation_4.png){fig-alt="Confounded Association Between `X` and `Y` due to a Common Cause, `Z`."}

Confounded Association Between `X` and `Y` due to a Common Cause, `Z`.
:::

@@

::: {#fig-reliabilityVsValidity}
![](images/reliabilityVsValidity.png){fig-alt="Reliability Versus Validity."}

Reliability Versus Validity.
:::

>>>>

This chapter provides an overview of key concepts in research methods.
These considerations are crucial for designing studies and for interpreting findings from research studies.

@@

::: {#fig-correlationAndCausation1}
![](images/correlationAndCausation_1.png){fig-alt="Hypothesized Causal Effect Based on an Observed Association Between `X` and `Y`, Such That `X` Causes `Y`. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Hypothesized Causal Effect Based on an Observed Association Between `X` and `Y`, Such That `X` Causes `Y`. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-correlationAndCausation2}
![](images/correlationAndCausation_2.png){fig-alt="Reverse (Opposite) Direction of Effect From the Hypothesized Effect, Where `Y` Causes `X`. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Reverse (Opposite) Direction of Effect From the Hypothesized Effect, Where `Y` Causes `X`. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-correlationAndCausation3}
![](images/correlationAndCausation_3.png){fig-alt="Bidirectional Effect Between `X` and `Y`, such that `X` causes `Y` and `Y` causes `X`. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Bidirectional Effect Between `X` and `Y`, such that `X` causes `Y` and `Y` causes `X`. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-correlationAndCausation4}
![](images/correlationAndCausation_4.png){fig-alt="Confounded Association Between `X` and `Y` due to a Common Cause, `Z`. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Confounded Association Between `X` and `Y` due to a Common Cause, `Z`. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::

@@

::: {#fig-reliabilityVsValidity}
![](images/reliabilityVsValidity.png){fig-alt="Reliability Versus Validity. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Reliability Versus Validity. From @Petersen2024a and @PetersenPrinciplesPsychAssessment.
:::
